\iffalse
\title{2022}
\author{EE24BTECH11012}
\section{mcq-single}
\fi
%\begin{enumerate}
	\item A plane P is parallel to two lines whose direction ratios are $\myvec{-2,1,3}$ and $\myvec{-1,2,-2}$ and it contains the point $\myvec{2,2,-2}$. Let P intersect the co-ordinate axes at the points A, B, C making the intercepts $\alpha$, $\beta$, $\gamma$. If $\vec{V}$ is te volume of the tetrahedron OABC, where O is the origin and $p=\alpha + \beta + \gamma$, then the ordered pair $\myvec{\vec{V}, p}$ is equal to :\hfill{[July 2022]}
		\begin{enumerate}
				\begin{multicols}{4}
				\item $\myvec{48,-13}$
				\item $\myvec{24,-13}$
				\item $\myvec{48,11}$
				\item $\myvec{24,-5}$
				\end{multicols}
		\end{enumerate}
	\item Let S be the set of all $ a \in \vec{R}$ for which the angle between the vectors $\vec{u} = a\brak{\log_{e}{b}}\vec{i} -6\vec{j} + 3\vec{k}$ and $\vec{v} = \log_{e}{b}\vec{i} + 2\vec{j} + 2a\log_{e}{b}\vec{k}$, $(b>1)$ is acute. Then S is equal to \hfill{[July 2022]}
		\begin{enumerate}
				\begin{multicols}{4}
				\item $\brak{-\infty, -\frac{4}{3}}$
				\item $ \phi $
				\item $\brak{-\frac{4}{3}, 0}$
				\item $\brak{\frac{12}{7}, \infty}$
				\end{multicols}
		\end{enumerate}
	\item A horizontal park is in the shape of a triangle OAB with AB = 16. A vertical lamp post OP is erected at the point O such that $\angle{PAO} = \angle{PBO} = 15 \degree$ and $\angle{PCO} = 45\degree$, where C is the mid-point of AB. Then $\brak{OP}^2$ is equal to \hfill{[July 2022]}
		\begin{enumerate}
				\begin{multicols}{4}
				\item $\frac{32}{\sqrt{3}}\brak{\sqrt{3}-1}$
				\item $\frac{32}{\sqrt{3}}\brak{2-\sqrt{3}}$
				\item $\frac{16}{\sqrt{3}}\brak{\sqrt{3}-1}$
				\item $\frac{16}{\sqrt{3}}\brak{2-\sqrt{3}}$
				\end{multicols}
		\end{enumerate}
	\item Let A and B be two events such that $P(B|A) = \frac{2}{5}$, $P(A|B) = \frac{1}{7}$ and $P(A \cap B) = \frac{1}{9}$. Consider \\
		\textbf{S1} : $P(A^{\prime} \cup B) = \frac{5}{6} $ \\
		\textbf{S2} : $P(A^{\prime} \cap B^{\prime}) = \frac{1}{18} $    \hfill{[July 2022]}
		\begin{enumerate}
			\item Both S1 and S2 are true .
			\item Both S1 and S2 are false.
			\item S1 is true, but S2 is false.
			\item S1 is false, but S1 is true.
		\end{enumerate}
	\item Let \\
		\textbf{p} : Ramesh listens to music. \\
		\textbf{q} : Ramesh is out of his village. \\
		\textbf{r} : It is Sunday. \\
		\textbf{s} : It is Saturday. \\
		Then the statement "Ramesh listens to music only if he is in his village and it is Sunday or Saturday" can be expressed as \hfill{[July 2022]}
		\begin{enumerate}
				\begin{multicols}{2}
				\item $\brak{\brak{\neg{q}} \land \brak{r \lor s}} \implies p $
				\item $\brak{q \land \brak{r \lor s}} \implies p$
				\item $p \implies \brak{q \land \brak{r \lor s}}$
				\item $p \implies \brak{\brak{\neg{q}} \land \brak{r \lor s}}$
				\end{multicols}
		\end{enumerate}
%\end{enumerate}
%\end{document}
